cardinalR: Generating interesting high-dimensional data structures

### 2025-10-22 paper-cardinalR.Rmd
Updated Figure 7 title

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data. Each shows variations in curvature, density, and continuity. Various geometric forms captured by the trigonometric shape generators, illustrating how different non-linear geometric structures can challenge to test the robustness of algorithms.", fig.width=12, fig.height=16, out.width="100%", fig.align='center', fig.pos="H"}

>>>>

```{r triginometric-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data. The `curvycylinder` shows a cylindrical manifold with a nonlinear twist along its height, producing smooth, continuous curvature. The `sphericalspiral` traces a spiral path on a spherical surface, combining circular and vertical motion in a helical form. The `conicspiral` expands radially while ascending, forming a conical helix with twisting variations in a non-radial dimension. The `nonlinear` dataset exhibits a warped 2D surface with sharp oscillations and smooth waves, reflecting complex nonlinear interactions. Each shows variations in curvature, density, and continuity.", fig.width=12, fig.height=16, out.width="100%", fig.align='center', fig.pos="H"}

### 2025-10-22 paper-cardinalR.tex
Updated Figure 7 title

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data. Each shows variations in curvature, density, and continuity. Various geometric forms captured by the trigonometric shape generators, illustrating how different non-linear geometric structures can challenge to test the robustness of algorithms.}\label{fig:triginometric-proj}
\end{figure}

>>>>

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `curvycylinder` (a1-a3), `sphericalspiral` (b1-b3), `conicspiral` (c1-c3), and `nonlinear` (d1-d3) data. The `curvycylinder` shows a cylindrical manifold with a nonlinear twist along its height, producing smooth, continuous curvature. The `sphericalspiral` traces a spiral path on a spherical surface, combining circular and vertical motion in a helical form. The `conicspiral` expands radially while ascending, forming a conical helix with twisting variations in a non-radial dimension. The `nonlinear` dataset exhibits a warped 2D surface with sharp oscillations and smooth waves, reflecting complex nonlinear interactions. Each shows variations in curvature, density, and continuity.}\label{fig:triginometric-proj}
\end{figure}
